%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MSc in Mechatronics} % Degree
    {Hochschule Ravensburg-Weingarten} % Institution
    {Weingarten (Würt), Deutschland} % Location
    {2009 - 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Theory of Mechatronic system development. (V-Model development, Simulation based development, Test Driven Development).}
        \item {Design of Mathematical models for simulations.}
        \item {Motion Control algorithms for mobile-robots and six-axis robots.}
        \item {Programming \& Applications of Sensors and Actuators.}
        \item {application of OpenCV as sensors.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {B.E in Electronics and Communication} % Degree
    {Visveswaraya Technological University} % Institution
    {Bangalore, India} % Location
    {2002 - 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Basics of Digital and Analog circuit design.}
        \item {Learn Computer architecture, focusing on micro-controller \& DSP programming.}
        \item {Analog and Digital Filter Design.}
        \item {Got first taste for GNU/Linux and open-source development. Was active participant in spreading GNU/Linux evangelism and GNU/Linux awareness within my department by holding install-fests and gcc usage tutorials.}
        \item {Thesis: Designed PIC micro-controller based system basedDesign a system to wake up and notify a passenger individually on arrival of his/her destination for a transport firm.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
