%---------------------------------------------------------
% Novell.
%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {Novell Software Development. Ltd.} % Organization
    {Bangalore, India} % Location
    {Sept. 2006 - Oct. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Joined the team responsible for the maintanence \& development of eDirectory LDAP Server.}
      \item {contribute fixes towards libSAL (platform abstraction library used in eDirectory), work on libSAL gave me a chance to teach myself OS fundamentals, understand commonalities and differences between}
    	  \subitem {OS's : HP-UX, AIX, SOLARIS 9, Linux, Netware.}
	  \subitem {CPU architectures: x86, SPARC, PowerPC.}
	  \item {Design and deploy an inhouse test harness.}
	  \subitem {- Split the harness into multiple classes, each class representing a component in test-environment. Write clean interface APIs between each component. Test-Logic were themselves defined as objects based on test-case class thereby preventing the lab-environment details leaking into the test-logic.}
      \subitem {- Usage of Event loops based design pattern implement server component of harness which watched for the build events, pulled a build as soon it was ready, install the builds on test machines, execute the test-objects and push results into a database.}
      \subitem {- This was the first take on deploying continuous integration inside the department.}
	  \item {Begin development of a LDAP Proxy server as a member of a small team.}
	  \subitem {- Obtain the requirements from the Product owner \& architect to design components for the server using bottom up and Test Driven Development approach.}
	  \subitem {- Components: load-balancer, re-create LDAP trees on the fly, connection statistics component.}
	  \subitem {- Lead the automated test development for integration tests right from the start of the project.}
	  \subitem {- breakdown the entire task of quality into tiny tasks with effort estimations, dependencies and identify the sprints the tasks would go into.}
	  \subitem {- constantly add features to test framework to automatically publish and generate analytics from the test-results.}
	  \item {Contribute to kerneljanitors with tiny fixes to Linux kernel.}
       \end{cvitems}
    }