%---------------------------------------------------------
% NOKIA
%---------------------------------------------------------
  \cventry
    {Embedded Platform Software Architect} % Job title
    {Nokia Mobile Networks} % Organization
    {Ulm, Deutschland} % Location
    {May. 2016 - PRESENT} % Date(s)
    {%
		\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {As a lead Architect for platform component, collaborate with product-management, planners, vendors and developers on a new board introduction into the product porfolio:}
			\subitem {Analyze new HW architecture in relevance to the product requirements.}
			\subitem {break down System requirements to platform requirements.}
			\subitem {Identify the affected platform sub-components or define new sub-components needed to satisfy product requirments for new HW design.}
			\subitem {Help planners to map the design into work-packages, effort estimations and also map dependencies between individual work-packages.}
			\subitem {Collaborate with SoC Vendors and communicate our necessary requirments to be delivered in silicon and suporting BSPs.}
		\item {As a Hardware-Software Architect, co-ordinate with the HW team to align for a final clean hardware design which in synergy with software architecture.}
			\subitem {focus on targeting faster time to market with more software re-use.}
			\subitem {support newer boards on an older software release already made available to customer.}
		\item {Design of new customer features:}
			\subitem {The new Features are software additions/improvements requested by different programs to existing products that have already been shipped out.}
			\subitem {Co-ordinate feature development activity as a memeber of virtual teams spread across multiple physical Development sites of Nokia.}
		\item {Work on Feasibility Studies and Proof-of-Concepts}
		\item {Provide consultation to factory on creation of support scripts for flashing and certificate generation on a new board introduction.}
		\end{cvitems}
    }
  \cventry
    {Embedded Platform Software Developer} % Job title
    {Nokia Mobile Networks} % Organization
    {Ulm, Deutschland} % Location
    {May. 2013 - 2019} % Date(s)
    {%
		\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developer for Nokia's customized Linux From Scratch (LFS) distribution for its eNodeB.}
		\item {Maintainer of FPGA subsystem in Linux kernel: implement user-space libraries, kernel drivers to manage FPGA life-cycle. Also managed packaging of FPGA firmwares within Platform Software release cycles.}
		\item {As a bootloader developer, implement nokia customizations on top of uBoot and AMI-BIOS for startup including signed-verified-boot.}
		\item {Debug and fix problems in user-space tools and relevant kernel modules to sign installed Software, generate board private certificates, verify installed Software during startup.}
		\item {Import, Integrate and Maintain yet to be upstreamed patches to open source components provided by vendors.}
		\item {Actively debug and work on various board interconnect technologies like PCIe, sRIO and ethernet.}
		\item {Redesign startup of LFS from SysV to systemd in migration to systemd.}
		\item {Collect analytics from Continous Integration to analyze platform performance.}
		\end{cvitems}
  }
