%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Early Member of BLUG.} % Affiliation/role
    {BLUG - Bangalore Linux Users Group (Developers’ Network for Linux)} % Organization/group
    {Bangalore, India} % Location
    {2004 - 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
       \item {Now a defunct group, was a platform to share open-source work from developers across the city.}
       \item {An active volunteer in first two FOSS.IN events.}
       \item {promote GNU/Linux by hosting installfest's in my campus.}
      \end{cvitems}
    }

%---------------------------------------------------------
	\cventry
    {Organizer} % Affiliation/role
    {eDirectory day} % Organization/group
    {Ulm, Deutschland} % Location
    {2006 - 2008} % Date(s)
    {
    	  \begin{cvitems}
    	    \item {Organize and host annual hackfest inside Novell to promote awareness and unique applications of LDAP directory.}
    	  \end{cvitems}
    }


%---------------------------------------------------------
	\cventry
    {Volunteer} % Affiliation/role
    {Indians in Ulm } % Organization/group
    {Ulm, Deutschland} % Location
    {2015 - } % Date(s)
    {
    	  \begin{cvitems}
    	    \item {Co-ordinate and organize annual Indian Celebrations in Ulm. A platform for Indians to meetup and grow their Network in the city.}
    	  \end{cvitems}
    }

%---------------------------------------------------------
	\cventry
    {Volunteer} % Affiliation/role
    {Ulmer Garage - Building a Maker-space within Nokia} % Organization/group
    {Ulm, Deutschland} % Location
    {2016 - } % Date(s)
    {
    	  \begin{cvitems}
    	    \item {contribute some spare time towards building a Maker space within Nokia's Ulm site, hosting events to promote maker culture.}
    	  \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\begin{cvskills}
%---------------------------------------------------------
\cvskill
	{Hobbies} % Category
	{Photography, Graphic Design, Collect Music} % Skills

%---------------------------------------------------------
\cvskill
	{Outdoor Activities} % Category
	{Football, Hiking \& Camping, Squash} % Skills
\end{cvskills}
