%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects and Thesis}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Master Thesis: Implementation of Simulation Models of  Mobile Robots as Plants inside LABVIEW} % Job title
    {Hochschule Ravensburg-Weingarten} % Organization
    {Weingarten, Deutschland} % Location
    {May. 2010 - Sept. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Study of few mobile robots available in our lab and derive its mathematical properties, implement them as LABVIEW models. Dr.-Ing Bern Altmann was intending to use LabVIEW to simulate and perform theoretical studies on different control strategies.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Scientific Project: Design of a Hardware Test Bench to simulate Engine input into a Gearbox} % Job title
    {Hochschule Ravensburg-Weingarten} % Organization
    {Weingarten, Deutschland} % Location
    {Jan. 2010 - Jul. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities      
        \item {Design \& implementation of simulation testbench using a single-board computer controlling a DC drive.}
        \item {Objective was to simulate the input of an engine to a gearbox. Later the testbench was purposed as a Hardware-in loop simulation environment to develop ”Gearshift by wire” implementation for Formula Student.}
      \end{cvitems}
    }
   
%---------------------------------------------------------
  \cventry
    {Research Project: Design a Control algorithm for a robotic mobile platform} % Job title
    {Hochschule Ravensburg-Weingarten} % Organization
    {Weingarten, Deutschland} % Location
    {Oct. 2009 - Dec. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Derive a simple model \& design a digital controller for the mobile robot designed to be used as a transporter on a factory floor.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Research Project: Personalized Passenger Alter System on Destination arrival in Long distance bus Multi-Stop Night Journeys} % Job title
    {BTL Institue of Technology} % Organization
    {Bangalore, India} % Location
    {Dec. 2005 - Sept. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Requirement: Design a system to wake up and notify a passenger individually on arrival of his/her destination instead of calling out destination names loudly inside the bus as done in rural India.}
      	\item {Solution was split into into two modules}:
      	\subitem {- module1: an eeprom stores two tables, one table of destinations in the route along with its GPS co-ordinates, second table that maps seats to its destinations (based on booking data), thereby mapping passengers to their respective destinations.}
      	\subitem {- at the start of the journey driver plugs module1 into module2.}
      	\subitem {- module2: continuously acquire GPS data and actuate wake-up elements on seats (based on data obtained from module 1) to indicate arrival of destination.}
      	\item {Design and implement a small proof of concept both modules based on PIC uC and tiny DC drive vibrators fixed into armrests as actuators to keep costs low.}
      	\item {Document the work}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
