%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Adapted to
% https://github.com/hemanthgu/Awesome-CV
% Adaptations by:
% Hemanth Guruva Reddy <meethemanth@gmail.com>
%
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\input{hemanth_data/personalinfo.tex}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {ASML Netherlands}
  {Veldhoven, The Netherlands}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Embedded Software Engineer - SW DE ES Positioning and Immersion}
% How the letter is opened
\letteropening{Dear Recruiter,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Hemanth Guruv Reddy~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

It's with great enthusiasm that I submit my application for "Embedded Developer in Positioning and Immersion" position as an embedded developer with over 8+ years of experience. I know my diverse skills and qualifications will make me an asset at ASML.

As you will see from the attached resume, I've built my career in variety of roles and industries, mostly as part of team in large scale system development. During my career I've not only just wrote code as programmer but also actively contributed towards hardware-software interface and device driver architecture, help in sprint planning by deriving task dependencies, initiate discussions with component vendors and customers to complete the requirements when missing, also being a lasting friend to my co-workers. I'm not only used to wearing multiple hats, I sincerely enjoy it.

In addition to being flexible and responsive, You need someone who's committed to high standards and is willing to adjust, change or completely redo current code to find the best way of implementing functions, and who lives and breathes embedded systems and robotics. And since all of that is my bread and butter. I'm thrilled at the possibility of being involved with ASML, a company which is deeply committed to its R\&D, developing products by having a strong customer and supplier relationships during its life-cycle. 

An opportunity to work and learn with best minds in mechatronics from multiple disciplines has come almost at the moment when ASML is upgrading its product code-base to make use of new languages. Which means challenging days are ahead. Would like to meet and discuss the value that I could add into the team. I appreciate your consideration and look forward to hear from you.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
